Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-08 journal paper/content/sec-theory-proofs.tex
Moved proofs to the appendix.

\subsubsection{Main result on \HardMax: Proof of Theorem~\ref{thm:DG-dominance}}
\label{sec:proofs-HM-main}

@@

%%%%%%%%%%%%
\subsubsection{\HardMax with biased tie-breaking: 
Proof of Theorem~\ref{thm:HardMax-biased}}
\label{sec:proofs-HM-main}

@@

%%%%%%%%%%%%
\subsubsection{The main result for \HardMaxRandom:
Proof of Theorem~\ref{thm:random-clean}}
\label{sec:proofs-HMR-main}

@@

%%%%%%%%%%%%
\subsubsection{For \HardMaxRandom, a little greedy goes a long way
(Proof of Theorem~\ref{thm:random-greedy})}
\label{sec:proofs-HMR-main}

@@

%%%%%%%%%%%%
\subsubsection{\SoftMaxRandom: proof of Theorem~\ref{thm:SoftMax-strong}}
\label{sec:proofs-SoftMax}

>>>>

\subsection{Main result on \HardMax: Proof of Theorem~\ref{thm:DG-dominance}}
\label{sec:proofs-HM-main}

@@

%%%%%%%%%%%%
\subsection{\HardMax with biased tie-breaking:
Proof of Theorem~\ref{thm:HardMax-biased}}
\label{sec:proofs-HM-main}

@@

%%%%%%%%%%%%
\subsection{The main result for \HardMaxRandom:
Proof of Theorem~\ref{thm:random-clean}}
\label{sec:proofs-HMR-main}

@@

%%%%%%%%%%%%
\subsection{For \HardMaxRandom, a little greedy goes a long way
(Proof of Theorem~\ref{thm:random-greedy})}
\label{sec:proofs-HMR-main}

@@

%%%%%%%%%%%%
\subsection{\SoftMaxRandom: proof of Theorem~\ref{thm:SoftMax-strong}}
\label{sec:proofs-SoftMax}
